Lord Vorotron: Finding the Best JFA Variant for the Coming Winter

### 2020-09-17 paper/main.tex
for Kamil
table fix
table reduction + colab run + latex fix

%%% BONUS %%%
%\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
\usepackage[bottom]{footmisc}% for footnotes
\usepackage{tabularx, booktabs}
\newcolumntype{L}{>{\raggedright\footnotesize}m{6cm}}
\renewcommand{\arraystretch}{1.2}
%%%%%%%%%%%%%

%%% BIBTEX %%%
% https://sunsite.icm.edu.pl/pub/CTAN/info/biblatex-cheatsheet/biblatex-cheatsheet.pdf
%\usepackage[backend=bibtex, style=numeric, sorting=ynt]{biblatex}
%\addbibresource{main.bib} %                       `ynt` vs. `ydnt`
%\newcommand{\citep}[1]{\citeauthor*{#1} \cite{#1}} % for `fancy` cite style
%%%%%%%%%%%%%%

\newcommand{\ourjfasingle}{JFAStar}
\newcommand{\ourjfa}{Lord Vorotron} % okJFAuto / JFAstar
%\title{A survey of \emph{jump flooding algorithm} applied to Voronoi}
% \emph{\ourjfa}: Evolving Fast GPU Algorithm for
% Voronoi Diagram and Distance Transform in O(1) from JFA using AutoML
\title{lord vorotron: finding the best JFA variant for the coming winter} % $\approx$

%\renewcommand{\headeright}{}
%\renewcommand{\undertitle}{Draft}
%\renewcommand{\shorttitle}{\ourjfa}

%\date{September 9, 1985}	% Here you can change the date presented in the paper title
%\date{} 					% Or removing it

\author{Maciej A. Czyzewski}
\affiliation{%
 \institution{Poznan University of Technology}
 \city{Poznan}
 \country{Poland}}

\author{Kamil Piechowiak}
\affiliation{%
 \institution{Poznan University of Technology}
 \city{Poznan}
 \country{Poland}}

@@

\hl{\textbf{UWAGA!} Przenioslem fragmenty ze starego szkicu, teraz jednak czuje ze
powinnien byc to takie ogolne podsumowanie wszystkich mozliwych wariantow JFA - i
w jakich przypadkach sie sprawdzaja. A tak przyokazji nasza wersja z szumem+trikami
ktora dobrze dziala, no i dodatek taki ze mozna teraz zrobic sobie ensembla (a
nie jako glowny cel tej pracy). Dlatego wszystko co ponizej to praktycznie
random/bardzo mocny szkic. Wykresy to wizualizacja smaku.}
\newline

@@

@@

\hl{\textbf{CEL:} omawiamy dwa algorytmy? jeden nastepca JFA} -
\textbf{\ourjfasingle} \hspace{0.01cm} \hl{oraz ensembla po naszym score fn. -}
\textbf{\ourjfa}???????

\keywords{aaaaaaaaaaaaaaaaaa \and bbbbbbbbbbbbbbb \and ccccccccccccccccccc}

@@

\begin{enumerate}
	\item Presenting new state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: \newline
		\textbf{\ourjfasingle} - single best variant;
		\textbf{\ourjfa} - ensemble of weak variants; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

@@

\begin{table}[H] \centering
\begin{tabular}{@{}lllll@{}}
\toprule
Reference                & Algorithm    & Exactness   & Time         & Work         \\ \midrule
\citep{de2017fast}       & FastGPU      & Exact       & $O(n^3/p)$   & -            \\
\citep{cao2010parallel}  & PBA          & Exact       & $O(n)$       & $O(mN)$      \\
\citep{honda2017simple}  & based on SKW & Exact       & $O(n)$       & $O(N)$       \\
\citep{manduhu2019work}  & WTO          & \cellcolor{blue!25}\textbf{Exact}& \cellcolor{blue!25}$\bm{O(\log n)}$  & $O(N)$       \\
\citep{schneider2009gpu} & SKW          & Approximate & $O(n)$       & $O(N)$       \\
\citep{rong2006jump}     & JFA          & Approximate & $O(\log n)$  & $O(N\log n)$ \\ \bottomrule
In this paper            & \ourjfa      & \cellcolor{blue!25}\textbf{Approximate} & \cellcolor{blue!25}$\sim$$\bm{O(1)}$ & $\sim$$O(N)$ \\ \bottomrule
\end{tabular}
\vspace{1em}
\caption{Different GPU algorithms for computing EDT}
\end{table}

@@

Aby badania byly bardziej przejrzyste trzymalismy sie pewnej konfencji
nazewniczej:

$$
[\bm{anchor\_type}][\bm{anchor\_num}][\bm{anchor\_double}]\qquad|\qquad[\bm{step\_function}]\qquad+\qquad[\bm{noise}]
$$

dla przykladu \textit{Circle11(1/3)Dual(1/4)|Factor3+Noise} ktore mozna
przeczytac jako:

\begin{multline}
anchor\_type=Circle, anchor\_num=11, anchor\_number\_ratio=1/3, \\
anchor\_double=True, anchor\_distance\_ratio=1/4, \\
step\_function=Factor3, noise=True
\end{multline}

@@

\subsubsection{Anchor Num} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\subsection{Multi-domain Algorithm (JFAStar)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Ensemble Across Domains (Vorotron)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%% BONUS %%%
%\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
\usepackage[bottom]{footmisc}% for footnotes
\usepackage{tabularx, booktabs}
\newcolumntype{L}{>{\raggedright\footnotesize}m{5.75cm}}
\renewcommand{\arraystretch}{1.2}
%%%%%%%%%%%%%

\usepackage{listings}
\lstset{
  language=Python,
  basicstyle=\footnotesize\ttfamily,
  captionpos=b,
  breaklines=false,
  escapeinside={(*}{*)},
  keywordstyle=\color{blue},
  tabsize=2,
  showspaces=false,
  breakatwhitespace=true,
  showstringspaces=false,
  columns=fullflexible,
  %numbers=left,
  numbersep=3pt,
  showtabs=false,
  %numberstyle=\scriptsize\ttfamily\color{mygray},
  morekeywords={string,foreach,var,async,await,lock},
  frame=TB
}

\newcommand{\ourjfasingle}{JFAStar}
\newcommand{\ourjfa}{Vorotron} % okJFAuto

% \title{A survey of \emph{jump flooding algorithm} applied to Voronoi}
% \emph{\ourjfa}: Evolving Fast GPU Algorithm for
% Voronoi Diagram and Distance Transform in O(1) from JFA using AutoML

% https://capitalizemytitle.com/
\title{Lord Vorotron: Finding the Best JFA Variant for the Coming Winter} % $\approx$

\author{Maciej A. Czyzewski}
\email{maciejanthonyczyzewski@gmail.com}
\affiliation{%
 \institution{Poznan University of Technology}
 \city{Poznan}
 \country{Poland}}

\author{Kamil Piechowiak}
\email{kamil.cams@gmail.com}
\affiliation{%
 \institution{Poznan University of Technology}
 \city{Poznan}
 \country{Poland}}

@@

% \hl{\textbf{UWAGA!} Przenioslem fragmenty ze starego szkicu, teraz jednak czuje ze
% powinnien byc to takie ogolne podsumowanie wszystkich mozliwych wariantow JFA - i
% w jakich przypadkach sie sprawdzaja. A tak przyokazji nasza wersja z szumem+trikami
% ktora dobrze dziala, no i dodatek taki ze mozna teraz zrobic sobie ensembla (a
% nie jako glowny cel tej pracy). Dlatego wszystko co ponizej to praktycznie
% random/bardzo mocny szkic. Wykresy to wizualizacja smaku.}
% \newline

\hl{\textbf{UWAGA}: wymyslic prawidlowa nazwe pracy + poprawic zlozonosci +
opisac dwa algorytmy}

@@

% http://dl.acm.org/ccs.cfm

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010371</concept_id>
<concept_desc>Computing methodologies~Computer graphics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10010061</concept_id>
<concept_desc>Theory of computation~Randomness, geometry and discrete structures</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010169</concept_id>
<concept_desc>Computing methodologies~Parallel computing methodologies</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003809.10010031</concept_id>
<concept_desc>Theory of computation~Data structures design and analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Computer graphics}
\ccsdesc[300]{Theory of computation~Randomness, geometry and discrete structures}
\ccsdesc[500]{Computing methodologies~Parallel computing methodologies}
\ccsdesc[500]{Theory of computation~Data structures design and analysis}

\keywords{Voronoi Diagram, Distance Transform, Code Generation}

@@

@@

\begin{enumerate}
	\item Presenting new state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: \newline
		\textbf{\ourjfasingle} - (Multi-domain) single best variant;
		\textbf{\ourjfa} - (Specific-domain) ensemble of weak variants; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

@@

\begin{table}[H] \centering
\begin{tabular}{@{}lllll@{}}
\toprule
Reference                & Algorithm    & Exactness   & Time         & Work         \\ \midrule
\citep{de2017fast}       & FastGPU      & Exact       & $O(n^3/p)$   & -            \\
\citep{cao2010parallel}  & PBA          & Exact       & $O(n)$       & $O(mN)$      \\
\citep{honda2017simple}  & based on SKW & Exact       & $O(n)$       & $O(N)$       \\
\citep{manduhu2019work}  & WTO          & \cellcolor{blue!25}\textbf{Exact}&
	\cellcolor{blue!25}$\mathbf{O(\log n)}$  & $O(N)$       \\
\citep{schneider2009gpu} & SKW          & Approximate & $O(n)$       & $O(N)$       \\
\citep{rong2006jump}     & JFA          & Approximate & $O(\log n)$  & $O(N\log n)$ \\ \bottomrule
In this paper            & \ourjfasingle&
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(\log^{\ast} n)}$ & $\sim$$O(N)$ \\
                         & \ourjfa      &
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(1)}$ & $\sim$$O(N)$ \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Different GPU algorithms for computing EDT}
\end{table}

@@

Aby badania byly bardziej przejrzyste trzymalismy sie pewnej konfencji
nazewniczej:
$$
[\bm{anchor\_type}][\bm{anchor\_num}][\bm{anchor\_double}]\qquad|\qquad[\bm{step\_function}]\qquad+\qquad[\bm{noise}]
$$

dla przykladu \longvar{Circle11(1/3)Dual(1/4)|Factor3+Noise} ktore mozna
przeczytac jako:

\begin{flalign*}
	\text{[anchor\_type]}=Circle, \\
	\text{[anchor\_num]}=11, \\
	\text{[anchor\_number\_ratio]}=1/3, \\
	\text{[anchor\_double]}=True, \\
	\text{[anchor\_distance\_ratio]}=1/4, \\
	\text{[step\_function]}=Factor3, \\
	\text{[noise]}=True
\end{flalign*}

@@

\subsubsection{Anchor Number} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{lstlisting}
def mod_step_function__special(shape, num=None, config=None):
    # [EXAMPLE]
    # Special(1.51/0.92/0.92/1.08/0.42)
    # ------- A -- B -- C -- D -- X ---

    A = config["A"]  # <1,   2>
    B = config["B"]  # <0,   1>
    C = config["C"]  # <0,   1>
    D = config["D"]  # <1,   2>
    X = config["X"]  # <0.2, 1>

    q = num / (shape[0] * shape[1])
    qm = ((shape[0] + shape[1]) / 2) * q**(1 / 2)
    S = B * qm + (1 - B) * (max(shape) / 2)
    St = math.log2(S)

    steps = []
    for i in range(1, int(X * St * 2), 1):
        f = round(1 / (D**(i**A) + i % max(1, int(C * St))), 4)
        ffm = int(f * S)
        if ffm >= 1:
            steps.append(ffm)
    if len(steps) == 0:
        return [1]

    return steps
\end{lstlisting}

@@

\subsection{Multi-domain Algorithm (\ourjfasingle)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Ensemble Across Domains (\ourjfa)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
